Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-12 arxiv/transfer.tex
sec

\section{Bias-Variance Decomposition, Same Covariates Setting}
%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g. Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
%Our main technical contribution is to extend this result to two tasks.
%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
We describe our result for the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
We extend the bias-variance decomposition from the two-task case to the multiple-task case.
Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
\begin{align}
	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
\end{align}
One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
Compared to the prediction loss of single-task learning (cf. equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.

Our main result for the multiple-task case provides generalization bounds that relate the empirical bias and variance of multi-task learning to the sample size $n$ and the distance between task models.
Before stating the result, we define the following notations.
Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.

\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	Consider the multiple-task case where all tasks have the same covariates.
	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
	Then, the following is true:
	\begin{itemize}
		\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
		 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
		\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
		\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
	\end{itemize}
\end{theorem}
Theorem \ref{thm_many_tasks} provides a sharp analysis of the bias-variance tradeoff in the multiple-task case.
As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
The proof of \ref{thm_many_tasks} can be found in Section \ref{app_proof_many_tasks}.

	First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
	Recall that all tasks have the same covariates in this setting.
	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
	\begin{align}
		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
	\begin{align*}
		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
	\end{align*}
	Recall that $\hat{B}_t^{\MTL} = \hat{B} W_t$, and we obtain equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple} by a decomposition of the expected prediction loss over the random noise condition on $X$ as follows
	\begin{align}
		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
	\end{align}
	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
	One can see that the first part of the last equation is the bias and the second part is the variance.
	Hence the proof is complete.

	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we also obtain the objective $g(\cW)$.
	\begin{align}
		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2. \label{eq_mtl_output_layer}
	\end{align}
	Now we are ready to prove Theorem \ref{thm_many_tasks}.
	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.

%As a remark, since the spectral norm of $U_r$ is less than $1$, we have that $\norm{U_r(i)} < 1$ for all $1 \le i \le t$. Compared to Theorem \ref{thm_main_informal}, we can get a simple expression for the two functions $\Delta_{vari}$ and $\Delta_{\bias}$. The proof of Theorem \ref{thm_many_tasks} can be found in Appendix \ref{app_proof_many_tasks}.

%In this section we consider the setting with $k$ many that have the same covariates.
%Since every task has the same number of data points as well as the same covariance, the only differences between different tasks are their models $\set{\beta_i}_{i=1}^k$.
%For this setting, we derive solutions for the multi-task training and the transfer learning setting that match our insights qualitatively from Section \ref{sec_denoise}.
%Using Lemma \ref{lem_minv} and some concentration bounds, we can complete the proof of Theorem \ref{thm_many_tasks}.

@@

	\medskip
	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
	Next, we show that the concentration errors of $g_0(\cW), g_1(\cW), g_2(\cW)$ are all lower order terms compared to $\ex{g(\cW)}$.

	First, for $g_1(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for a sufficiently small constant $\e>0$, the following holds with high probability:
	\[ \text{for any } 1\le j \le t, |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|. \]
	%and
	%\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
	%&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
	%\end{align*}
	Applying the above estimates into $g_1(\cW)$, we get that
	\begin{align}
	  \abs{g_1(\cal W)}    &\le p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \nonumber \\
	&\le  p^\e \sigma \sum_{j=1}^t \bignorm{  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \cdot \|Z\| \nonumber\\
	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \bignorm{  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)} \nonumber\\
	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + t\sigma^2 p^{1/2+\e}.  \label{eq_est_g1}
	\end{align}
	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we use equation \eqref{eq_isometric} to bound the operator norm $\|Z\|$ by $\OO(\sqrt{p})$.
	In the last step, we use the AM-GM inequality.

	Second, for $g_2(\cW)$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we obtain that for any $1\le i, j \le t$, the following holds with high probability:
	\begin{align*}
		\bigabs{\norm{\varepsilon_j}^2 - \ex{\norm{\varepsilon_j}^2}} &\le \sigma^2 p^{1/2+\e},\\
		%|\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|
		\abs{W_i^{\top} (\cW\cW^{\top})^{-1} W_j \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}}
		&\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \bigtr{(U_X U_X^{\top})^2}^{1/2} \le \sigma^2 p^{1/2+\e}
  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
  % &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
  % &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
	\end{align*}
	Combining the above two inequalities together, we get that with high probability
	\begin{align}
		\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}. \label{eq_est_g2}
	\end{align}

	Finally, for $g_0(\cW)$, denote by $v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right)$, for any $j = 1,\dots,t$, we have that $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}.
	Hence by law of large numbers, we have that with high probability
	${\left\|Z v_j \right\|^2 } = { n \|v_j\|^2} \cdot (1+\oo(1))$,
	which implies that
	\begin{align}
		g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)). \label{eq_est_g0}
	\end{align}

	Combining equation \eqref{eq_est_g1}, \eqref{eq_est_g2}, and \eqref{eq_est_g0}, we obtain that with high probability
	\begin{align}
	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e}) \nonumber \\
	&=\ex{g(\cW)} \cdot (1+\oo(1)) + \OO(\sigma^2 p^{1/2+\e}). \label{eq_est_g}
	\end{align}

>>>>

\section{Bias-Variance Decomposition, Same Covariates Setting}
%A well-known result in the high-dimensional linear regression setting states that $\tr[(X_2^{\top}X_2)^{-1}\Sigma_2]$ is concentrated around $1 / (\rho_2 - 1)$ (e.g. Chapter 6 of \cite{S07}), which scales with the sample size of the target task.
%Our main technical contribution is to extend this result to two tasks.
%We show how the variance of the multi-task estimator scales with sample size and covariate shift in the following result.
We begin by considering the multiple-task case where all tasks have the same covariates, that is, $X_i = X$, $n_i = n$, and $\Sigma_i = \Sigma$ for all $i = 1, \dots, t$.
%This setting is prevalent in applications of multi-task learning to image classification, where there are multiple prediction labels/tasks for every image \cite{chexnet17,EA20}.
%We consider an arbitrary local minimum $B, W_1, \dots, W_2$ of the optimization objective.
%We extend the bias-variance decomposition from the two-task case to the multiple-task case.
%We observe that the expected prediction loss of $\hat{\beta}_t^{\MTL}$ conditional on $X$ consists of a bias and a variance equation as follows
%\begin{align}
%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{\beta}_t^{\MTL}) \mid X}
%	=& \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t}}^2 \label{eq_bias_multiple} \\
%	&+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top} X)^{-1}} \label{eq_var_multiple}
%\end{align}
%One can see that equation \eqref{eq_bias_multiple} is the bias of the multi-task learning estimator and equation \eqref{eq_var_multiple} is its variance.
%Compared to the prediction loss of single-task learning (cf. equation \eqref{eq_var_stl}), we observe that the variance equation \eqref{eq_var_multiple} is always smaller because $W_t^{\top} (\cW \cW^{\top})^{-1} W_t \le 1$.
%On the other hand, the bias equation \eqref{eq_bias_multiple} is always larger because of the difference between the task models.
We show the generalization error of hard parameter sharing estimators.
Before stating the result, we define the following notations.
Let $B^\star := [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
Let $U_r U_r^{\top}$ denote the best rank-$r$ subspace approximation of $(B^{\star})^\top\Sigma B^{\star}$, that is,
\[ U_r \define \argmin_{X\in\real^{t\times r} : X^{\top} X = \id_{r\times r}} \inner{X X^{\top}} {B^{\star} \Sigma B^{\star}}. \]
For $i = 1,\dots, t$, let $v_i \in\real^r$ denote the $i$-th row of $U_r$.
Our main result in this section is stated as follows.

\begin{theorem}[Multiple-task case with the same covariates]\label{thm_many_tasks}
%Suppose $X=Z\Sigma^{1/2}\in \R^{n\times p}$ satisfy Assumption \ref{assm_secA1} with $\rho:=n/p>1$ being some fixed constant. Consider data models  $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $\e_i\in \R^{n}$ are random vectors with i.i.d. entries with mean zero, variance $\sigma^2$ and all moments as in \eqref{assmAhigh}. Moreover, assume that $X$, $\beta_i$ and $\e_i$ are all independent of each other.
	%Let $n = c \cdot p$.
	%Let $X\in\real^{n\times p}$ and $Y_i = X\beta_i + \varepsilon_i$, for $i = 1,\dots,k$.
%	Consider $t$ data models $Y_i = X\beta_i + \varepsilon_i$, $i=1,2,\cdots, t$, where $X$ has covariance matrix $\Sigma$, and the entries of $\e_i$ are i.i.d. with mean zero and variance $\sigma^2$.
	%that satisfy Assumption \ref{assm_secA2} in the appendix.
	Consider the multiple-task case where all tasks have the same covariates.
	Assume that $\lambda_{\min}({B^{\star}}^\top\Sigma B^{\star})\gtrsim \sigma^2$.
	Let $\delta$ be any fixed value such that $\delta \le \oo \left( \|B^\star\|^2 + \sigma^2\right)$.
	Then, for any task $i$ from $1$ to $t$, the prediction loss of the hard parameter sharing estimator satisfies that
	\begin{align}
		\bigabs{L(\hat{\beta}_i^{\MTL}) - \norm{\Sigma^{1/2} (B^{\star} U_r v_t - \beta_t)}^2 - \norm{v_t}^2 \frac{\sigma^2}{\rho - 1}} \le o(\bigtr{{B^{\star}}^{\top}\Sigma B^{\star}} + \sigma^2).
	\end{align}
	%\begin{itemize}
	%	\item \textbf{Positive transfer:} If $\left(1 - \norm{v_t}^2 \right)\frac{\sigma^2}{\rho - 1} -  > \delta$, then w.h.p over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
	%	 \[ \te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL}). \]
	%	\item \textbf{Negative transfer:} If $\left(1 - \norm{v_t}^2\right)\frac{\sigma^2}{\rho - 1} - \norm{\Sigma^{1/2}(B^{\star} U_r v_t - \beta_t)}^2 < -\delta$, then w.h.p. over the randomness of $X, \varepsilon_1, \dots, \varepsilon_t$, we have that
	%	\[ \te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL}). \]
	%\end{itemize}
\end{theorem}
	Theorem \ref{thm_many_tasks} provides a sharp generalization error bound \todo{check}.
	As shown in the proof of Theorem \ref{thm_many_tasks}, the equation $(1 - \norm{v_t}^2)\frac {\sigma^2}{\rho - 1}$ is the amount of variance reduced using multi-task learning and $\norm{\Sigma (B^{\star} U_r v_t - \beta_t)}$ is the bias.
	\todo{check}

	%First, we provide the steps for showing the bias-variance decomposition in equation \eqref{eq_bias_multiple} and \eqref{eq_var_multiple}.
	The key idea for proving Theorem \ref{thm_many_tasks} is a bias-variance decomposition of the prediction loss of hard parameter sharing.
	We describe the idea in the following.
	Since all tasks have the same covariates, the optimization objective \eqref{eq_mtl} becomes
	\begin{align}
		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$. % for $1 < r < t$ by our assumption.
	Let $\cal W = [W_1, W_2, \dots, W_t] \in \real^{r\times t}$ be a matrix that contains all the parameters of the output layers.
	Using the local optimality condition over $B$, that is, $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
	\begin{align*}
		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
	\end{align*}
	Recall that $\hat{\beta}_t^{\MTL} = \hat{B} W_t$.
	The expected prediction loss over the random noise conditional on $X$ is equal to
	\begin{align}
		 & \exarg{\varepsilon_1, \dots, \varepsilon_t}{L(\hat{B}_t^{\MTL}) \mid X} \nonumber \\
		=& \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{\Sigma^{1/2} \bigbrace{B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1}W_t - \beta_t} + (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW \cW^{\top})^{-1} W_t}^2 \mid X} \nonumber \\
		=& \bignorm{\Sigma^{1/2} (B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_t - \beta_t)}^2
		+ \sum_{i=1}^t \bigtr{X (X^{\top}X)^{-1}\Sigma (X^{\top}X)^{-1}X^{\top} \exarg{\varepsilon_i}{\varepsilon_i \varepsilon_i^{\top}} (W_i^{\top} (\cW \cW^{\top})^{-1} W_t)^2} \nonumber \\
		=& \bignorm{\Sigma^{1/2}(B^{\star} \cW^{\top} (\cW \cW)^{-1} W_t - \beta_t)}^2
		+ \sigma^2 \cdot (W_t^{\top} (\cW \cW^{\top})^{-1} W_t) \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}. \label{eq_ex_pred}
	\end{align}
	The third step uses the fact that $\varepsilon_i$ consists of i.i.d. entries with mean zero and variance $\sigma^2$.
	The last step uses the fact that $\sum_{i=1}^t W_i W_i^{\top} = \cW \cW^{\top}$.
	One can see that the first part of the last equation is the bias and the second part is the variance.
	Hence the proof is complete.

	By plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov}, we obtain the objective $g(\cW)$ that only depends on the output layers.
	\begin{align}
		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2. \label{eq_mtl_output_layer}
	\end{align}
	We state a concentration error bound between $g(\cal W)$ and its expectation.

	\begin{lemma}\label{lem_error_same_cov}
		In the setting of Theorem \ref{thm_many_tasks}, we have that
		\[ g(\cW) = \ex{g(\cW)} \cdot (1 + o(1)) + \OO(\sigma^2 p^{1/2 + c}). \]
	\end{lemma}
	The proof of Lemma \ref{lem_error_same_cov} is via standard concentration bounds.
	The details can be found in Appendix \ref{app_proof_error_same_cov}.
	Based on the above result, we are ready to prove Theorem \ref{thm_many_tasks}.
	We use the notation $U_X U_X^{\top} = X (X^{\top} X)^{-1} X^{\top} \in\real^{n \times n}$ to denote the projection matrix to $X$, where $U_X\in\real^{n \times p}$.

@@
